### 2021-09-12 paper/output/document/paper31.tex
updated stuff

\ poss{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}poss{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isasymTurnstile}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline

@@

\ \ \isakeyword{assumes}\ poss{\isacharunderscore}murder{\isacharunderscore}wrong\isanewline
\ \ \isakeyword{shows}\ murder{\isacharunderscore}wrong\isanewline

@@

\ assms\ \isacommand{by}\isamarkupfalse%

@@

An initial property that we might be interested in is permissibility itself. More generally, an ethical
theory that doesn't allow for permissibility would require that every action is either obligatory or 
prohibited. In fact, if that is the case, many counterintuitive theorems follow, including that all 
permissible actions are obligatory.\footnote{Proof is in the appendix.}%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
}\isanewline
%
\isamarkupcmt{This is exactly the desired result above - we have shown that models exist where an action can be 
neither obligatory nor prohibited.%
}\isanewline
%
\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
obligatory in this theory, then clearly it doesn't track our intuitions.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:

@@

%:%233=130%:%
%:%236=131%:%
%:%240=131%:%
%:%241=131%:%

@@

%:%244=132%:%
%:%245=133%:%
%:%255=135%:%
%:%256=136%:%
%:%257=137%:%
%:%261=139%:%

@@

%:%267=143%:%

@@

@@

%:%271=144%:%

@@

%:%273=146%:%
%:%274=146%:%
%:%276=148%:%
%:%277=149%:%
%:%278=150%:%
%:%279=151%:%

@@

%:%282=153%:%
%:%283=154%:%

@@

%:%285=156%:%
%:%286=156%:%
%:%289=157%:%
%:%293=157%:%

@@

%:%296=158%:%
%:%297=159%:%

@@

%:%299=161%:%

@@

%:%302=162%:%
%:%303=163%:%
%:%304=164%:%

@@

%:%306=166%:%

@@

%:%309=167%:%
%:%310=168%:%
%:%320=170%:%
%:%321=171%:%
%:%322=172%:%
%:%323=173%:%
%:%324=174%:%
%:%325=175%:%
%:%326=176%:%
%:%327=177%:%

@@

%:%330=179%:%
%:%331=180%:%

@@

%:%333=182%:%
%:%334=182%:%
%:%336=182%:%
%:%340=182%:%

@@

%:%343=183%:%
%:%344=184%:%
%:%345=185%:%
%:%346=186%:%
%:%347=187%:%
%:%348=188%:%
%:%358=190%:%
%:%359=191%:%
%:%360=192%:%
%:%361=193%:%
%:%362=194%:%
%:%363=195%:%
%:%372=197%:%
%:%384=199%:%
%:%385=200%:%
%:%386=201%:%
%:%387=202%:%
%:%388=203%:%
%:%389=204%:%
%:%390=205%:%
%:%391=206%:%
%:%392=207%:%
%:%393=208%:%
%:%394=209%:%

@@

%:%397=212%:%

@@

%:%399=213%:%
%:%400=214%:%
%:%401=215%:%
%:%402=215%:%
%:%404=215%:%
%:%408=215%:%
%:%409=215%:%

@@

%:%412=217%:%
%:%413=218%:%
%:%414=219%:%
%:%415=219%:%
%:%417=220%:%
%:%418=221%:%
%:%419=221%:%
%:%421=222%:%
%:%422=223%:%
%:%432=225%:%
%:%433=226%:%
%:%435=228%:%
%:%436=228%:%
%:%437=229%:%
%:%438=230%:%
%:%439=231%:%
%:%440=231%:%
%:%442=231%:%
%:%446=231%:%
%:%447=231%:%
%:%449=232%:%
%:%450=233%:%
%:%451=234%:%
%:%452=235%:%
%:%453=235%:%
%:%455=236%:%

@@

%:%469=240%:%

@@

%:%471=242%:%
%:%472=243%:%
%:%474=245%:%
%:%475=245%:%
%:%476=246%:%
%:%477=247%:%
%:%478=248%:%
%:%479=248%:%
%:%481=248%:%
%:%485=248%:%
%:%486=248%:%
%:%488=249%:%
%:%489=250%:%
%:%490=251%:%
%:%491=252%:%
%:%492=252%:%
%:%494=253%:%

@@

%:%505=256%:%
%:%506=257%:%
%:%508=259%:%
%:%509=259%:%
%:%510=260%:%
%:%511=261%:%
%:%512=262%:%
%:%513=262%:%
%:%515=262%:%
%:%519=262%:%
%:%520=262%:%
%:%522=263%:%
%:%523=264%:%
%:%524=265%:%
%:%525=265%:%
%:%527=266%:%
%:%537=268%:%

@@

%:%539=270%:%
%:%541=272%:%

@@

%:%543=273%:%
%:%544=274%:%
%:%545=275%:%
%:%546=276%:%
%:%547=277%:%
%:%548=277%:%
%:%555=278%:%
%:%556=278%:%
%:%557=279%:%
%:%558=279%:%
%:%559=280%:%
%:%560=280%:%
%:%561=281%:%
%:%562=281%:%
%:%563=281%:%
%:%564=281%:%
%:%566=282%:%
%:%567=283%:%
%:%568=283%:%
%:%569=284%:%
%:%570=284%:%
%:%571=284%:%
%:%573=285%:%
%:%574=286%:%
%:%575=287%:%
%:%576=288%:%
%:%577=289%:%
%:%578=289%:%
%:%580=290%:%
%:%590=292%:%
%:%591=293%:%
%:%592=294%:%
%:%593=295%:%
%:%594=296%:%
%:%596=298%:%
%:%597=298%:%
%:%598=299%:%
%:%599=300%:%
%:%600=301%:%
%:%601=301%:%
%:%603=301%:%
%:%607=301%:%
%:%608=301%:%
%:%610=302%:%
%:%611=303%:%
%:%612=304%:%
%:%613=305%:%
%:%614=306%:%
%:%624=308%:%
%:%625=309%:%
%:%629=311%:%
%:%633=313%:%
%:%634=314%:%
%:%635=315%:%
%:%637=317%:%
%:%638=317%:%
%:%639=318%:%
%:%642=319%:%
%:%646=319%:%
%:%647=319%:%
%:%649=320%:%
%:%650=320%:%
%:%652=321%:%
%:%653=322%:%
%:%654=323%:%
%:%655=324%:%
%:%656=325%:%
%:%666=327%:%
%:%667=328%:%
%:%668=329%:%
%:%669=330%:%
%:%671=332%:%
%:%672=332%:%
%:%673=333%:%
%:%676=334%:%
%:%680=334%:%
%:%681=334%:%
%:%682=334%:%
%:%684=335%:%
%:%685=335%:%

>>>>

\ possibly{\isacharunderscore}murder{\isacharunderscore}wrong{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymequiv}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isachardoublequoteclose}\isanewline

@@

\ \ \isakeyword{shows}\ {\isachardoublequoteopen}possibly{\isacharunderscore}murder{\isacharunderscore}wrong\ {\isasymlongrightarrow}\ murder{\isacharunderscore}wrong{\isachardoublequoteclose}\isanewline

@@

@@

An initial property that we might be interested in is permissibility itself. More generally, an ethical
theory that doesn't allow for permissibility would require that every action is either obligatory or 
prohibited. In fact, if that is the case, many counterintuitive theorems follow, including that all 
permissible actions are obligatory.\footnote{Proof is in the appendix.}%
\end{isamarkuptext}\isamarkuptrue%
\ \ \isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:

  Skolem constant:
    A =($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{We want to show that there exists a model where there is some formula A that is permissible, or, 
in English, that permissibility is possible. Nitpick finds a model where the above formula holds, 
so permissibility is indeed possible.%
}\isanewline
%
\isamarkupcmt{Note that it's not clear \cite{kitcher} if Kant actually thought that permissibility was a coherent 
concept. Either way, in modern ethics, permissibility is a pretty widely accepted phenomenon.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ fixed{\isacharunderscore}formula{\isacharunderscore}is{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False)\color{black}%
}\isanewline
%
\isamarkupcmt{This is a slightly stronger result: for any arbitrary action A, there is a model that makes it 
permissible. We actually don't want this to hold, because if A is "murder" then the CI requires that 
it be prohibited in every world.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Another initial test is the possibility of arbitrary obligations. If anything can be shown to be 
obligatory in this theory, then clearly it doesn't track our intuitions.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O\ {\isacharbraceleft}A{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 1:

@@

%:%235=130%:%
%:%239=130%:%
%:%240=130%:%

@@

%:%243=132%:%
%:%253=134%:%
%:%254=135%:%
%:%255=136%:%
%:%259=138%:%
%:%261=140%:%
%:%262=140%:%

@@

@@

%:%269=143%:%

@@

%:%271=145%:%

@@

%:%274=147%:%
%:%275=148%:%
%:%276=149%:%
%:%277=150%:%
%:%279=152%:%
%:%280=152%:%

@@

%:%282=154%:%
%:%283=155%:%

@@

%:%287=156%:%
%:%291=156%:%
%:%292=156%:%

@@

%:%295=158%:%
%:%296=159%:%
%:%297=160%:%

@@

@@

%:%301=162%:%
%:%302=163%:%
%:%303=164%:%
%:%304=165%:%

@@

@@

%:%308=167%:%
%:%318=169%:%
%:%319=170%:%
%:%320=171%:%
%:%321=172%:%
%:%322=173%:%
%:%323=174%:%
%:%324=175%:%
%:%325=176%:%
%:%327=178%:%
%:%328=178%:%

@@

%:%330=180%:%
%:%331=181%:%

@@

%:%334=181%:%
%:%338=181%:%
%:%339=181%:%

@@

%:%342=183%:%
%:%343=184%:%
%:%344=185%:%
%:%345=186%:%
%:%346=187%:%
%:%356=189%:%
%:%357=190%:%
%:%358=191%:%
%:%359=192%:%
%:%360=193%:%
%:%361=194%:%
%:%370=196%:%
%:%382=198%:%
%:%383=199%:%
%:%384=200%:%
%:%385=201%:%
%:%386=202%:%
%:%387=203%:%
%:%388=204%:%
%:%389=205%:%
%:%390=206%:%
%:%391=207%:%
%:%392=208%:%
%:%393=209%:%

@@

%:%396=210%:%
%:%397=211%:%

@@

%:%399=212%:%
%:%401=212%:%
%:%405=212%:%
%:%406=212%:%
%:%408=213%:%
%:%409=214%:%
%:%410=215%:%

@@

%:%412=216%:%
%:%414=217%:%
%:%415=218%:%
%:%416=219%:%
%:%417=219%:%
%:%419=220%:%
%:%420=221%:%
%:%428=221%:%
%:%429=222%:%
%:%430=223%:%
%:%431=223%:%
%:%432=224%:%
%:%433=225%:%
%:%434=226%:%
%:%435=226%:%
%:%437=226%:%
%:%441=226%:%
%:%442=226%:%
%:%444=227%:%
%:%445=228%:%
%:%446=229%:%
%:%447=230%:%
%:%448=230%:%
%:%450=231%:%
%:%451=232%:%
%:%452=233%:%
%:%462=235%:%
%:%463=236%:%

@@

%:%466=238%:%
%:%467=239%:%
%:%468=240%:%
%:%469=241%:%

@@

%:%472=241%:%
%:%476=241%:%
%:%477=241%:%
%:%479=242%:%
%:%480=243%:%
%:%481=244%:%
%:%482=245%:%
%:%483=245%:%
%:%485=246%:%
%:%495=248%:%
%:%499=250%:%
%:%500=251%:%
%:%501=252%:%
%:%502=253%:%

@@

%:%505=255%:%
%:%506=256%:%
%:%507=257%:%
%:%508=258%:%
%:%509=258%:%
%:%511=258%:%
%:%515=258%:%
%:%516=258%:%
%:%518=259%:%
%:%519=260%:%
%:%520=261%:%
%:%521=262%:%
%:%522=262%:%
%:%524=263%:%
%:%534=265%:%
%:%535=266%:%
%:%536=267%:%

@@

%:%539=269%:%
%:%540=270%:%
%:%541=271%:%

@@

%:%543=272%:%
%:%545=272%:%
%:%549=272%:%
%:%550=272%:%
%:%552=273%:%
%:%553=274%:%
%:%554=275%:%
%:%555=275%:%
%:%557=276%:%
%:%567=278%:%
%:%568=279%:%
%:%569=280%:%
%:%571=282%:%
%:%572=282%:%
%:%573=283%:%
%:%574=284%:%
%:%575=285%:%
%:%576=286%:%
%:%577=287%:%
%:%578=287%:%
%:%585=288%:%
%:%586=288%:%
%:%587=289%:%
%:%588=289%:%
%:%589=290%:%
%:%590=290%:%
%:%591=291%:%
%:%592=291%:%
%:%593=291%:%
%:%594=291%:%
%:%596=292%:%
%:%597=293%:%
%:%598=293%:%
%:%599=294%:%
%:%600=294%:%
%:%601=294%:%
%:%603=295%:%
%:%604=296%:%
%:%605=297%:%
%:%606=298%:%
%:%607=299%:%
%:%608=299%:%
%:%610=300%:%
%:%620=302%:%
%:%621=303%:%
%:%622=304%:%
%:%623=305%:%
%:%624=306%:%
%:%626=308%:%
%:%627=308%:%
%:%628=309%:%
%:%629=310%:%
%:%630=311%:%
%:%631=311%:%
%:%633=311%:%
%:%637=311%:%
%:%638=311%:%
%:%640=312%:%
%:%641=313%:%
%:%642=314%:%
%:%643=315%:%
%:%644=316%:%
%:%654=318%:%
%:%655=319%:%
%:%659=321%:%
%:%663=323%:%
%:%664=324%:%
%:%665=325%:%
%:%667=327%:%
%:%668=327%:%
%:%669=328%:%
%:%672=329%:%
%:%676=329%:%
%:%677=329%:%
%:%679=330%:%
%:%680=330%:%
%:%682=331%:%
%:%683=332%:%
%:%684=333%:%
%:%685=334%:%
%:%686=335%:%
%:%696=337%:%
%:%697=338%:%
%:%698=339%:%
%:%699=340%:%
%:%701=342%:%
%:%702=342%:%
%:%703=343%:%
%:%706=344%:%
%:%710=344%:%
%:%711=344%:%
%:%712=344%:%
%:%714=345%:%
%:%715=345%:%
